Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-08-01 paper.qmd

plot_effects_all
```

>>>>

plot_effects_all
```
Our confirmatory results revealed strong positive significant main effects of sex-specific strength on partnered status, numbers of lifetime partners after controlling for all five sets of potential confounds. There was no significant effect of sex-specific strength on the number of partners in the past year, and there were inconsistent effects of sex-specific strength on age at first sex across the potential confound models.

Unlike findings from the pilot study, a clear sex difference in the effects of sex-specific strength only emerged for one mating success outcome---partnered status---with smaller effects for women compared to men, as predicted by the sexual selection hypothesis. The interaction between sex and sex-specific strength on lifetime number of sexual partners was not replicated in the confirmatory data.  Finally there was no evidence for a sex difference in the effects of sex-specific strength on past year number of partners or age at first sex, contrary to the sexual selection hypothesis.

Effects of sex-specific standardized strength on mating outcomes, by sex. Strength is centered and scaled by 2 SD, separately for each sex (almost all participants therefore fall between -1 and 1). Plots are based on the anthropometric control models, with control variables held at their mean values. Lifetime partners is modeled as the rate of new partners per year since reaching sexual maturity (age 12).

## Discussion
The purpose of this study was to replicate as closely as possible, the results from @lassek2009, in new data that included women and used combined grip strength as a proxy for upper body strength. We found consistent support for a positive relationship between combined grip strength and two measures of mating success: being currently partnered, and lifetime number of sexual partners for both men and women, controlling for numerous possible confounds. We found no consistent association between strength and age at first sex or number of past year sexual partners.

We also tested for interactions between sex and strength on these mating success outcomes. Across both pilot and confirmatory data, we found a consistent interaction between sex and strength on partnered status, such that grip strength was more important for predicting males' partnered status than females. Although in the pilot data we did see evidence of an interaction between sex and strength on the outcome lifetime number of sexual partners, such that strength was more important for predicting males' lifetime sexual partners, this effect was not present in the confirmatory data.
